Combined annotation exploration for SCPCP000006

### 2024-11-14 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
fix logic bug, re-render

# Create a data frames of all annotations
cell_type_df <- sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      # These samples were run with "none" as the reference
      none_reference_samples <- c("SCPCS000177", "SCPCS000180", "SCPCS000181", "SCPCS000190", "SCPCS000197")
      if (sample_id %in% none_reference_samples) {
        reference <- "none"
      } else {
        reference <- "both"
      }

@@

      # The file may not be present if this is being run in CI, so check first
      # We should error out if the file does not exist and we are NOT testing
      if (!file.exists(input_file) & !params$testing) {
        stop("input RDS file not found.")
      }

>>>>

# These samples were run with "none" as the reference
none_reference_samples <- c("SCPCS000177", "SCPCS000180", "SCPCS000181", "SCPCS000190", "SCPCS000197")

# Create a data frames of all annotations
cell_type_df <- sample_ids |>
  purrr::map(
    # For each sample_id, do the following:
    \(sample_id) {
      if (sample_id %in% none_reference_samples) {
        reference <- "none"
      } else {
        reference <- "both"
      }

@@

      # The file may not be present if this is being run in CI, which is ok.
      # If we are not running in CI and the file doesn't exist, we should error out
      # We should error out if the file does not exist and we are NOT testing
      if (!file.exists(input_file)) {
        if (params$testing) {
          return(NULL)
        } else {
          stop("Input RDS file does not exist.")
        }
      }
